---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
library(ggplot2)
```

##Binomial
The package `"binomial"` is a minimal R package that creates binomial variables and does some easy summary about the binomial variable.

##Creating the Binomial Variable
```{r}
bv<-bin_variable(trials=10,prob=0.5)
```

##Print the Varable and Summary
```{r}
bv
summary(bv)
```

##Get Distribution
You can get the distribution of the binomial variable.
```{r}
bin_distribution(trials=10,prob=0.5)
bin_cumulative(trials=10,prob=0.5)
```

##Plots
You can use plot() function to plot the barplot of the probabilities against success and plot of cumulative probability against success. 
```{r}
plot(bin_distribution(trials=10,prob=0.5))
plot(bin_cumulative(trials=10,prob=0.5))
```

##Calculate the Statistics
```{r}
bin_choose(5,1)
bin_mean(5,0.5)
bin_variance(5,0.5)
bin_mode(5,0.5)
bin_skewness(5,0.5)
bin_kurtosis(5,0.5)
```

